---
title: "Homework10"
author: "Brian Pham, bp26834, https://github.com/bpham010/SDS315-Homework10"
date: "2024-04-10"
output:
  pdf_document: default
  html_document: default
---


```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=4, fig.width=6, warning=FALSE, tidy=TRUE, message = FALSE, tidy.opts=list(width.cutoff=60))
```



```{r, echo = FALSE, results = 'hide'}


library(readr)
library(mosaic)
library(moderndive)

redlining <- read_csv("~/SDS315/Homework10/redlining.csv")


redlineLM = lm(policies ~ minority + fire + age + income, data=redlining)
get_regression_table(redlineLM)


```

1). We are trying to answer the question of whether or not there is an association between the number of FAIR policies and the racial/ethnic composition of a ZIP code after adjusting fire, age, and income variables. 

2). A multiple linear regression model was used to generate a regression model for the above variables. Then, a regression table was generated using the model for further analysis. 

3). According to the regression table, we are 95% confident that there is a slight association between the number of FAIR polices and the racial/ethnic composition of a ZIP code with a correlation between 0.003 and 0.14 which is statistically significant as the values do not contain 0. 

4). In conclusion, there is a high likelihood of a positive correlation between the number of FAIR polices and the racial/ethnic composition of a ZIP code. For stakeholders this could mean the differences between deciding to invest resources into a ZIP code or not.


# Problem 2: Grocery Store Prices



### Part A
```{r, echo = FALSE}
library(ggplot2)
library(tidyverse)
library(mosaic)
library(moderndive)
library(effectsize)


groceries <- read_csv("~/SDS315/Homework10/groceries.csv")

groceriesGroupedStore <- groceries %>%
  group_by(Store) %>%
  summarize(meanPrices = mean(Price), n = n())

ggplot(data = groceriesGroupedStore, aes(x=Store, y=meanPrices)) + geom_bar(stat = 'identity') + coord_flip()
```

The graph above depicts the average price of items across different grocery stores. 



### Part B

```{r, echo = FALSE}
groceriesGroupedProduct = groceries %>%
  group_by(Product) %>%
  summarize(sumProduct = n())

#groceriesGroupedProduct


ggplot(data = groceriesGroupedProduct, aes(x=Product, y = sumProduct)) + geom_bar(stat = "identity") + coord_flip()

```

The bar graph above depicts each grocery item (listed on the y-axis) and the number of stores that sell that product (shown on the x-axis). 


### Part C

```{r, echo = FALSE, results = 'hide'}

typeLM = lm(Price ~ Product + Type, data=groceries)

get_regression_table(typeLM)

```

Compared with ordinary groceries stores (like Albertsons, HEB, or Krogers), convenience stores somewhere between .40 and .92 dollars more for the same product. 


### Part D

```{r, echo = FALSE, results = 'hide'}

priceLM = lm(Price ~ Product + Store, data = groceries)

get_regression_table(priceLM)
# best guess confidence intervals overlap
priceLM

```

On average, it appears that Walmart and Kroger Fresh Fare charge the highest prices when comparing the same products. 



# Part E

Between the two given possibilities, it appears that the theory that "Central Market charges a similar amount to HEB for the same product. The difference in estimated price of product between Central Market and HEB approximately .072 dollars. This difference is minuscule when comparing other ordinary stores such as Target and Fiesta which have a difference of .33 dollars. 



# Part F

```{r, echo = FALSE, results = 'hide'}
groceriesIncome = groceries %>%
  mutate(Income10K = Income/10,000)
  

incomePriceLM = lm(Price ~ Product + Income10K, data = groceriesIncome)

incomePriceLM


get_regression_summaries(incomePriceLM)
standardize_parameters(incomePriceLM)


```


On average, consumers in poorer ZIP codes tend to pay less for the same product since the main effect of Income10K yields 1.409e-05 less than expected when the Income10K variable is isolated. 



A one-standard deviation increase in the income of a ZIP code seems to be associated with
a 0.03 standard-deviation change in the price that consumers in that ZIP code expect to pay for the same product.


